% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% CV.tex
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Kedar Dabhadkar}
\newcommand{\CVTitle}{Kedar Dabhadkar's CV}
\newcommand{\CVNote}{CV compiled on {\today}}
\newcommand{\CVWebpage}{https://dkedar.com}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
\href{https://www.google.com/maps/place/2619+First+Avenue,+Seattle,+WA+98121,+USA}
{2615 First Avenue, Seattle, WA 98121, USA}
\par
\href{mailto:kdabhadk@gmail.com}
{kdabhadk@gmail.com}
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\url{\CVWebpage}}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% Experience %%
%%%%%%%%%%%%%%%
\Section
{Experience}
{Experience}
{PDF:Experience}

\Entry
\href{http://www.revelconsulting.com/}
{\textbf{Revel Consulting}},
Seattle, WA
\Entry
\textbf{Associate Data Scientist}
\hfill
\DatestampYMD{2019}{03}{11} --
present

\Gap
\BulletItem
Microsoft | Information Protection and Governance
\SubBulletItem
Provided Microsoft managers key insights into managing high-risk supplier engagements and proposed solutions to reduce the risk of non-compliance using Natural Language Processing (NLP), applied machine learning, and data visualizations in Power BI.
\SubBulletItem
Analyzed textual comments using unsupervised NLP to extract themes and understand root causes of engagement risk.
\SubBulletItem
Developed machine learning predictive models to proactively identify the type of risk associated with engagements.

\BulletItem
Microsoft | Proactive Recommendations
\SubBulletItem
Recommendation engine proof of concept to proactively recommend workshops, seminars to thousands of Microsoft customers.
\SubBulletItem
Addressed cold-start problems by matching customer attributes, comments in the open-cases with product description and past recommendations.

\BulletItem
Revel | Internal Projects
\SubBulletItem
Actively contributed to building and improving Data Science and Big Data Engineering technical screens using predictive modeling techniques and tools like Docker, PySpark.

\SubBulletItem
Conceptualizing positioning of Revel as a leader in data science and AI consulting by identifying key use-cases and building proof of concepts in computer vision, natural language processing and time series analysis.

\BigGap

% Experience 2
\Entry
\href{http://cmu.edu/cheme}
{\textbf{Carnegie Mellon University and Air Liquide S.A.}},
Pittsburgh, PA
\Entry
\textbf{Graduate Researcher}
\hfill
\DatestampYMD{2017}{12}{11} --
\DatestampYMD{2019}{02}{11}

\Gap
\BulletItem
Air Liquide S.A. | Data-driven Modeling of Reactor Temperature Profiles
\SubBulletItem
Collaborated with Air Liquide S.A. to develop statistical methods to model performance of reactors.
\SubBulletItem
Modeled process data using ARIMA with exogenous parameters (ARIMAX), NARX time-delayed neural networks and LSTM Recurrent Neural Networks (RNN).
\SubBulletItem
Empowered Air Liquide engineers with the capability to forecast performance of two key reactors.
\SubBulletItem
Assisted transition to data-driven methods from traditional methods by laying down the framework and building data pipeline.
\SubBulletItem
Presented this work at ‘Enterprise-Wide Optimization’, Pittsburgh, PA and it was also presented, on my behalf, at the conference ‘Big Data and Process Engineering: Opportunities and Limits’, Paris, France.

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\href{http://www.cmu.edu/}
{\textbf{Carnegie Mellon University}},
Pittsburgh, PA, USA

\Gap
\BulletItem
Master of Science (M.S.). in
\href{http://www.cmu.edu/cheme}
{Chemical Engineering}
\hfill
\DatestampYMD{2017}{08}{15} --
\DatestampYMD{2018}{12}{15}
\begin{Detail}
\SubBulletItem
Thesis:
{Data-driven Modeling of Reactor Temperature Profiles}
\SubBulletItem
Advisor:
Prof.~Nikolaos~Sahinidis
\SubBulletItem
Focus:
Sequential Data Modeling, Time Series Analysis, Data Science, Deep Learning.
\SubBulletItem
Cumulative GPA: 3.74 / 4.00
\end{Detail}

\BigGap
\Entry
\href{http://www.ictmumbai.edu.in/}
{\textbf{Institute of Chemical Technology}},
Mumbai, India

\Gap
\BulletItem
Bachelor of Chemical Engineering (B.Chem.Engg)
\hfill
\DatestampYMD{2013}{08}{15} --
\DatestampYMD{2017}{05}{15}
\begin{Detail}
\SubBulletItem
Final Project:
{Techno-economic Analysis of Condensing Water From Air}
\SubBulletItem
Advisor:
Prof.~V. H.~Dalvi
\end{Detail}

\BigGap
\Entry
{\textbf{Relevant Coursework:}}

Process Systems Modeling (06-665), Introduction to Machine Learning (10-601), Computer Science in Engineering (06-611), Applied Data Science (16-791), Introduction to Deep Learning (11-785), Mathematical Modeling in Chemical Engineering (06-623), Computational Methods (06-606), Project Economics (CET 1504).

\newpage

%%%%%%%%%%%%%%%%%%
%% PRESENTATIONS %%
%%%%%%%%%%%%%%%%%%

\Section
{Presentations}
{Presentations}
{PDF:Presentations}

\SubSection
{Conferences}
{Conferences}
{PDF:Conferences}

% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[88]}

\BigGap
\NumberedItem{[1]}
{\underline{K.~Dabhadkar}, K.~Ingale, N.~Sahinidis, E.~Ors, and M.~Mighani
``Data-Driven Modeling of Reactor Temperature Profiles,''
in \textit{Enterprise-Wide Optimization},
Pittsburgh,
PA,
USA,
\DatestampYM{2018}{11}.}


%%%%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%%%%

\Section
{Skills}
{Skills}
{PDF:Skills}

\textbf{Programming Languages}: \newline
Proficient: Python, R, SQL;  Intermediate: JAVA;	Basic: Bash, FORTRAN, C++, HTML.

\textbf{Software}: Apache Hive, Power BI, Tableau, MATLAB, GAMS.

\textbf{Databases}: PostgreSQL, MySQL, MSSQL.

\textbf{Packages}: Pandas, TensorFlow, PyTorch, Keras, scikit-learn, PySpark.

\textbf{Cloud Platforms}: AWS: Entire Stack; Azure: ML Services, ML Studio, VM; GCP: VM.

\textbf{Certifications}: AWS Certified Cloud Practitioner, Jul 2019

%%%%%%%%%%%%%%%%%%
%% PROJECTS %%
%%%%%%%%%%%%%%%%%%

\Section
{Projects}
{Projects}
{PDF:Projects}


\Entry
{\textbf{Analysis of Medical Records Using Natural Language Processing}},
Pittsburgh, PA
\hfill
\DatestampYM{2018}{06}
\Entry
\textit{Third Prize, Hackathon, North American Association of Central Cancer Registries (NAACCR)}
\BulletItem
Analyzed Electronic Medical Records (EMRs) of 10,000 cancer patients to identify tumor site.
\BulletItem
Scored an average F1 score of 0.91 on held-out data with an ensemble of Naïve Bayes, Random Forests and SVM.
\BulletItem
Presented applicability of such a system in practice to a group of physicians by demonstrating a web application.

\BigGap
\Entry
{\textbf{Pattern Recognition in Electroencephalogram (EEG) of Brain}},
Pittsburgh, PA
\hfill
\DatestampYM{2018}{03}
\Entry
\textit{First Prize, Hackathon, Auton Lab, Carnegie Mellon University and Phillips}
\BulletItem
Cleaned, pre-processed noisy EEG data to induce stationarity and transformed into a sequential matrix.
\BulletItem
Detected occurrence of Cyclic Alternating Pattern (CAP) with an Area Under the ROC (AUROC) of 58\% using logistic regression.
\BulletItem
Published methodology and results in an academic paper {\href{https://arxiv.org/abs/1804.08750}{ (https://arxiv.org/abs/1804.08750)}}.

\BigGap
\Entry
{\textbf{Extracting Information from Text}},
Pittsburgh, PA
\hfill
\DatestampYM{2017}{11}
\BulletItem
Built feature engineered logistic regression models to extract information from 50,000 sentences. 
\BulletItem
Deployed the program on an AWS EC2 p2.xlarge instance to parallelize computations using GPU.
\BulletItem
Improved average F1-score from 0.60 to 0.75 by feature modification using time-delay technique.

\BigGap
\Entry
{\textbf{Speaker Verification}},
Pittsburgh, PA
\hfill
\DatestampYM{2018}{10}
\BulletItem
Trained a Convolutional Neural Network (CNN) for speaker identification on 125 GB speech corpus.
\BulletItem
Extracted embedding from penultimate fully connected layer and compared speakers based on cosine similarity.
\BulletItem
Achieved EER (Equal Error Rate) of 13.7 \% on held-out data.

\BigGap
\Entry
{\textbf{Time Series Analysis of Currency Valuation}},
Pittsburgh, PA
\hfill
\DatestampYM{2017}{11}
\BulletItem
Implemented time-series analysis, descriptive statistics, various smoothing and stationarity induction methods, and autocorrelations to analyze valuation of the Indian National Rupee against the US Dollar.
\BulletItem
Employed web-scraping to perform live one-day-ahead predictions.
\BulletItem
Achieved a mean squared loss of 0.05 with ARIMA and improved it to 0.03 using an LSTM Recurrent Neural Network.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Awards \&\newline
Scholarships}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}

\BulletItem
Third Prize,
Cancer Informatics Hackathon,
NAACCR 2018 Annual Conference
\hfill
\DatestampYMD{2018}{06}{09}
\begin{Detail}
\Item
Natural Language Processing Model for Analysis of Medical Records.
\end{Detail}

\Gap
\BulletItem
First Prize,
HackAuton, Auton Lab, Carnegie Mellon University and Phillips
\hfill
\DatestampYMD{2018}{03}{07}
\begin{Detail}
\Item
Pattern Recognition in Electroencephalogram (EEG) of Brain.
\end{Detail}

\Gap
\BulletItem
Narotam Sekhsaria Foundation Postgraduate Scholarship
\hfill
\DatestampYM{2017}{05}
\begin{Detail}
\Item
For academic and co-curricular excellence
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL AFFILIATIONS & ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Professional Affiliations}
{Professional Affiliations}
{PDF:ProfessionalAffiliations}

\Entry
\href{http://www.siam.org/}
{\textbf{Society for Industrial and Applied Mathematics}}
\Gap
\BulletItem
Member
\hfill
\DatestampY{2017} --
Present

%%%%%%%%%%%%%%%%%%%%%%%
%% CAMPUS ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Campus Activities}
{Campus Activities}
{PDF:CampusActivities}

\Entry
\textbf{Treasurer, Technological Association},
Institute of Chemical Technology
\hfill
\DatestampY{2015} --
\DatestampY{2016}

\Entry
\textbf{Event Coordinator, ICT Marathon},
Institute of Chemical Technology
\hfill
\DatestampY{2014} --
\DatestampY{2015}

\Entry
\textbf{Coordinator, Awaaz- The Social Drive},
Institute of Chemical Technology
\hfill
\DatestampY{2014} --
\DatestampY{2015}

\end{Body}

\end{document}